---
title: "P8105_hw5_yc384"
author: 'Ying Chen (UNI: yc384)'
date: "11/5/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(readr)
library(ggridges)
library(purrr)
library(httr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
  
set.seed(10)

```

## Problem 1: The purpose of this problem is to fill in those missing values. 

* For numeric variables, replace missingness with the mean of non-missing values
* For character variables, fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r}
# Read in data
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
iris_missingreplaced = function(m) {
  
  if (is.numeric(m)) {
   replace_na(m, mean(m, na.rm = TRUE))
   }
   else if (is.character(m)) {
     replace_na(m, "virginica")
  } 
}

output = map_df(iris_with_missing, iris_missingreplaced)
output %>%
head(10) 

```


## Problem 2: Create a tidy dataframe containing all subject ID, arm, and observations over time and make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
## List all file names
files = list.files("./data", full.names = TRUE)

## Import data
data = map_df(files, read_csv)

## tidy
df = 
  data_frame(files) %>% 
  bind_cols(data) %>% 
  mutate(arm = substr(files, 8, 10),
         subject_ID = substr(files, 12, 13)) %>% 
  pivot_longer(week_1:week_8,
               names_to = "week",
               values_to = "obs") %>% 
  select(-files)


## making a spaghetti plot
plot1 = 
  df %>% 
  ggplot(aes(x = week, y = obs, group = subject_ID, color = arm)) +
  geom_line() + 
  stat_smooth(
    aes(group = 1),
    method = "lm"
    ) +
  labs(title = "Observations over Time for Each Subject",
       x = "Time in Weeks",
       y = "Observations") + 
  theme(legend.position = "none",  
        axis.text.x = element_text(hjust = 0.8, vjust = 0.5,                  
                       size = 6, angle = 25
        )) +
  facet_grid(. ~arm) 

plot1

```

**Comment:** From the spaghetti plot, we can see that the weekly observation for the experiment group increases as time increases; while the control arm decreased slightly overtime. Differenc in observation values between control and experiment groups increases overtime. The minimum value for the experiment group at week 8 is greater than the maximum value of the control group, which indicates the oberseved value at week 8 differs significantly. 

