---
title: "P8105_hw5_yc384"
author: 'Ying Chen (UNI: yc384)'
date: "11/5/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(readr)
library(ggridges)
library(purrr)
library(httr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
  
set.seed(10)

```

##Problem 1: The purpose of this problem is to fill in those missing values. 

* For numeric variables, replace missingness with the mean of non-missing values
* For character variables, fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r}
# Read in data
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
iris_missingreplaced = function(m) {
  
  if (is.numeric(m)) {
   replace_na(m, mean(m, na.rm = TRUE))
   }
   else if (is.character(m)) {
     replace_na(m, "virginica")
  } 
}

output = map_df(iris_with_missing, iris_missingreplaced)
output %>%
  view()
```
